---
title: "Analyis Bayesian Logistic Regression Models"
author: "Jens Hüsers"
date: "9/20/2019"
output:
  html_document:
    toc: true
editor_options: 
  chunk_output_type: console
---

TODO:

```{r setup, include=TRUE, warning=FALSE, message=FALSE}

knitr::opts_chunk$set(echo = TRUE,  
                      cache = TRUE,
                      warning = FALSE,
                      message = FALSE)

set.seed(2430024)

date <- lubridate::now()
format(date, "%a, %d. %B %Y")

# Load Packages
library(broman)
library(tidyverse)
library(knitr)
library(googlesheets4)
library(scales)
library(ggpubr)
library(magick)
library(gridExtra)
library(bayesplot)

# google sheets setup
googlesheet_id <- "1-0mfTM47nF2etqPqvcQzp9xspgTLNHjp-cZ0E1qGAjs"
sheets_auth(email = "jenshuesers@gmail.com")

# Import Local Package "PEDIS"
unloadNamespace("pedis")
devtools::load_all("~/r-projects/proj_wunde/pedis/")

# Data Import

pedis <- pedis::read_all_pedis("~/r-projects/proj_wunde/pedis-diabetic-care/datasets")

```

# Descriptive Tables

```{r}

desc_all <- descriptive_table_all(pedis)

sheets_write(data = desc_all,
             ss = googlesheet_id,
             sheet = "descr-table-all")

desc_any <- descriptive_table_outcome(pedis, outcome = "any_amputation")
sheets_write(data = desc_any,
             ss = googlesheet_id,
             sheet = "descr-table-any")

desc_maj <- descriptive_table_outcome(pedis, outcome = "major_amputation")
sheets_write(data = desc_maj,
             ss = googlesheet_id,
             sheet = "descr-table-maj")

```

# Model Setup

```{r}


# Setting model formula
f_any <- as.formula("any_amputation ~ p + e_ordinal_5 + d + i + s + alter_bei_aufnahme + gender")
f_major <- as.formula("major_amputation ~ p + e_ordinal_5 + d + i + s + alter_bei_aufnahme + gender")

# Setting priors

# Uninformed priors
uninformed_prior <- cauchy(location = c(rep(0, 5), 0, 0), scale = c(rep(1, 5), .5, .5))

source("./scripts/compute-informed-prior.R")

# Informed priors (from Pickwell et al.)
tibble(pooled_beta, pooled_sd) %>% 
  pivot_longer(cols = c("pooled_beta", "pooled_sd")) %>% 
  mutate(exp = exp(value)) %>% 
  set_names("statistic", "non-exponentiated", "exponentiated")

informed_prior <- cauchy(location = c(rep(pooled_beta, 5), 0, 0), scale = c(rep(pooled_sd, 5), .5, .5))

# Set number of MCMC interations
n_iter <- 8000
seed <- 3412

```

# Model Fitting

## Outcome: Any Amputation

### Non-Informed Prior

```{r, fig.height=10}

# Outcome: Any Amputation
# Approach: Non-Informed
noninformed_any <- fit_model(n_iter = n_iter, exponentiate = FALSE, seed = seed)

# Posterior Histogram with prior
errorbar_1 <- plot(noninformed_any[[1]]) + ggtitle("Non Informed Any")

# AUC Posterior
auc_noninformed_any <- posterior_auc(model = noninformed_any,
                                     data = pedis,
                                     outcome = "any_amputation")

```

### Informed Prior

```{r, fig.height=10}
# Outcome: Any Amputation
# Approach: Informed Prior

informed_any <- fit_model(formula = f_any, prior = informed_prior, n_iter = n_iter, seed = seed)

# Posterior histograms with priors
errorbar_2 <- plot(informed_any[[1]]) + ggtitle("Informed Any")

# AUC Posterior
auc_informed_any <- posterior_auc(model = informed_any,
                                  data = pedis,
                                  outcome = "any_amputation")

```

## Outcome: Major Amputation

### Non-Informed Prior

```{r, fig.height=10}
# Outcome: Any Amputation
# Approach: Informed Prior

noninformed_major <- fit_model(formula = f_major, n_iter = n_iter, seed = seed)

# Posterior Histogram with priors
errorbar_3 <- plot(noninformed_major[[1]]) + ggtitle("Non-Informed Major")

# AUC Posterior
auc_noninformed_major <- posterior_auc(model = noninformed_major,
                                       data = pedis,
                                       outcome = "major_amputation")

```

### Informed Prior

```{r, fig.height=10}
# Outcome: Major Amputation
# Approach: Informed Prior
informed_major <- fit_model(formula = f_major,
                            prior = informed_prior,
                            seed = seed,
                            n_iter = n_iter)

# Posterior histograms with priors
errorbar_4 <- plot(informed_major[[1]]) + ggtitle("Informed Major")

# AUC Posterior
auc_informed_major <- posterior_auc(model = informed_major,
                                    data = pedis,
                                    outcome = "major_amputation")

```

# AUCs

## AUC Descriptive Tables


```{r, eval = F}
# load stored MCMCs to save time in AUC claculation, when computation stays the same

files <- dir("models")
file <- files[grepl(x = files, pattern = "RDS$")]
filepath <- paste0("models/", file)

noninformed_any <- readRDS(filepath[1])
informed_any <- readRDS(filepath[2])
noninformed_major <- readRDS(filepath[3])
informed_major <- readRDS(filepath[4])

```


```{r}
auc <- list("Any Amputation - Non-Informed" = auc_noninformed_any, 
            "Any Amputation - Informed" = auc_informed_any, 
            "Major Amputation - Non-Informed" = auc_noninformed_major,
            "Major Amputation - Informed" = auc_informed_any)

# Descriptive Summary
auc_summarised <- map(auc, auc_summary) %>% 
  bind_rows(.id = "Model") %>% 
  mutate(HDI = paste0("[", myround(lower, 3), "-", myround(upper, 3), "]")) %>% 
  mutate_if(is.numeric, myround, 3)

auc_summarised %>%
  select(Model, med, HDI) %>% 
  kable(digits = 3)

sheets_write(data = auc_summarised,
             ss = googlesheet_id,
             sheet = "auc")
```

## AUC Posterior Distributions

```{r}

# Plot Posterior AUC Distributions

posterior_auc_distributions <- auc %>% map(hist, bw = .005) 

get_y_axis <- function(plt_obj) ggplot_build(plt_obj)$layout$panel_scales_y[[1]]$range$range

y_max <- map_df(posterior_auc_distributions, get_y_axis) %>% 
  pivot_longer(cols = names(.)) %>% 
  pull(value) %>% 
  max %>% 
  `+`(2)

x_min <- min(map_dbl(auc, quantile, .02)) 
x_max <- max(map_dbl(auc, max)) + .01

x_axis <- scale_x_continuous(name = "AUC value",
                             limits = c(x_min, x_max),
                             breaks = seq(0, 1, by = .02))

y_axis <- scale_y_continuous(name = "Density", limits = c(0, y_max))

g <- ggpubr::ggarrange(
  posterior_auc_distributions[[1]] + 
    x_axis + 
    y_axis +
    rremove("x.title"),
  posterior_auc_distributions[[2]] + 
    x_axis + 
    y_axis +
    rremove("x.title") +
    rremove("y.title"),
  posterior_auc_distributions[[3]] +
    x_axis + 
    y_axis,
  posterior_auc_distributions[[4]] +
    x_axis + 
    y_axis +
    rremove("y.title"),
  ncol = 2, 
  nrow = 2,
  labels = c("A", "B", "C", "D"))

g

ggsave(plot = g,
       filename = "img/posterior-auc-values.png",
       unit = "cm", width = 30, height = 30,
       dpi = 320,
       scale = .5)

```

# Posterior Parameter Distribution 

## Errorbars

```{r, fig.height=10, fig.width=10}

posterior_errorbars <- gridExtra::grid.arrange(
  errorbar_1 + scale_y_continuous(breaks = 0:10) + ggtitle("Any Amputation - Non-Informed."),
  errorbar_2 + scale_y_continuous(breaks = 0:10) + ggtitle("Any Amputation - Informed"),
  errorbar_3 + scale_y_continuous(breaks = 0:10) + ggtitle("Major Amputation - Non-Informed"),
  errorbar_4 + scale_y_continuous(breaks = 0:10) + ggtitle("Major Amputation - Informed"))

ggsave(posterior_errorbars,
       filename = "img/posterior-parameter-errorbars.png",
       unit = "cm",
       width = 20,
       height = 20)

```

## Descriptive Statistics

```{r}

models <- list("Any Amputation - Non-Informed" = noninformed_any, 
               "Any Amputation - Informed" = informed_any, 
               "Major Amputation - Non-Informed" = noninformed_major,
               "Major Amputation - Informed" = informed_major) 

summary_models <- map(models, summary_coefs) %>% 
  map(. %>% select(-model)) %>% 
  bind_rows(.id = "model") %>% 
  unite(col = "beta_coefficient",
        c("map_bayes_non-exponentiated", "hdi_char_non-exponentiated"),
        sep = " ") %>% 
  unite(col = "odds_ratio",
        c("map_bayes_exponentiated", "hdi_char_exponentiated"),
        sep = " ")
 
sheets_write(data = summary_models,
             ss = googlesheet_id,
             sheet = "coefficients")

```

## Parameter Posterior Distributions

```{r}

xlimit <- c(-1.2, 3)
ylimit <- c(0, 2.4)

hist_posterior <- models %>% 
  map(pluck, 3) %>% 
  map(function(x) x +
        # scale_x_continuous("Value of Coefficients", limits = c(-1.2, 3)) +
        theme(strip.text = element_text(size = 8),
              axis.text = element_text(size = 8)) +
        rremove("x.title") +
        rremove("y.title") +
        coord_cartesian(ylim = ylimit)
  )
  
hist_plot <- ggarrange(hist_posterior[[1]],
                       hist_posterior[[2]],
                       hist_posterior[[3]],
                       hist_posterior[[4]],
                       labels = LETTERS[1:4],
                       ncol = 4)

hist_plot

ggsave(plot = hist_plot,
       filename = "img/posterior-beta-values.png",
       unit = "cm", width = 22, height = 18,
       dpi = 300)

```

# Save RDS (Posterior Models)

```{r save-models, eval = F}

filename <- names(models) %>% 
  tolower %>% 
  gsub(pattern = "\\s+", replacement = " ") %>% 
  gsub(pattern = "\\s{1}", replacement = "-") %>% 
  gsub(pattern = "---", replacement = "-") %>% 
  paste0("models/", ., ".RDS")

map2(models, filename, saveRDS)

```

# Analysing the coefficients for major non-informed

In this section, I compute the proportion of posterior coefficient values that are smaller than 0.

The results show that most posterior values are postive. 
This fact supports the claim of a postive association between some predictors (PED)

```{r}

files <- dir("models")
file <- files[grepl(x = files, pattern = "major.*non.*RDS$")]

major_non_informed <- readRDS(paste0("models/", file))

prop_below_zero <- major_non_informed[[2]] %>% 
  mutate_all(function(x) x < 0) %>% 
  colSums()

prop_below_zero / 3e4

```



# Posterior Distribution of Predictions

Exemplary predictions of 6 month amputation incidence

```{r}

mat_mcmc <- noninformed_any[[2]] %>% as.matrix()

x1 <- mat_mcmc %*% c(intercept = 1, p = 2, e = 2, d = 1, i = 1, s = 1, age = 60, gender = 1) %>% 
  c %>%
  enframe(name = NULL) 
  
x2 <- mat_mcmc %*% c(intercept = 1, p = 3, e = 3, d = 3, i = 1, s = 1, age = 60, gender = 1) %>% 
  c %>% 
  enframe(name = NULL) 

data <- bind_rows(list("Patient with low PEDIS classification" = x1,
                       "Patient with high PEDIS classification" = x2),
                  .id = "patient") %>% 
  mutate(value = 1 / (1 + exp(-1 * value))) %>% 
  mutate(patient = factor(x = patient, 
                          levels = c("Patient with low PEDIS classification",
                                     "Patient with high PEDIS classification"),
                          labels = c("PEDIS classification: P2, E2, D1, I1, S1",
                                     "PEDIS classification: P3, E3, D3, I1, S1"),
                          ordered = TRUE))

mean_summary <- data %>% 
  group_by(patient) %>% 
  summarise(avg = mean(value), med = median(value))

predictions_summary <- data %>% 
  group_by(patient) %>% 
  nest() %>% 
  mutate(data = map(data, function(df) pull(df, 1))) %>% 
  mutate(hdi = map(data, function(x) tidy_hdi(x)),
         med = map_dbl(data, function(x) median(x)),
         avg = map_dbl(data, function(x) mean(x))) %>% 
  unnest(cols = c(hdi)) %>% 
  select(-data)

predictions_summary %>% 
  ggplot(aes(xmin = lower, xmax = upper, x = med, y = 1, group = patient)) +
  geom_histogram(aes(x = value,
                     y = ..density..,
                     fill = patient),
                 binwidth = .01,
                 data = data,
                 inherit.aes = FALSE) +
  geom_errorbarh(size = 1.5) +
  geom_point(shape = 20, size = 6) +
  scale_y_continuous("Density") +
  scale_x_continuous("Predicted risk (six-month amputation incidence)", 
                     breaks = seq(0, 1, by = .2),
                     limits = c(-.1, 1.05)) +
  ggtitle(label = "Posterior Distribution of Predictions",
          subtitle = "Predictions based on any-amputation risk model") +
  scale_fill_manual(values = c("grey50", "grey70")) +
  scale_color_manual(values = c("black", "black"), guide = F) +
  theme_minimal() +
  theme(title = element_text(size = 14),
        legend.position = "bottom",
        legend.direction = "vertical",
        legend.title = element_blank(), 
        text = element_text(size = 18))

ggsave(filename = "./img/post-amp-any-prob.png", units = "cm", width = 20, height = 20)

```

```{r}

mat_mcmc <- noninformed_major[[2]] %>% as.matrix()

x1 <- mat_mcmc %*% c(intercept = 1, p = 2, e = 2, d = 1, i = 1, s = 1, age = 60, gender = 1) %>% 
  c %>%
  enframe(name = NULL) 

x2 <- mat_mcmc %*% c(intercept = 1, p = 3, e = 3, d = 3, i = 1, s = 1, age = 60, gender = 1) %>% 
  c %>% 
  enframe(name = NULL) 

data <- bind_rows(list("Patient with low PEDIS Score" = x1,
                       "Patient with high PEDIS Score" = x2),
                  .id = "patient") %>% 
  mutate(value = 1 / (1 + exp(-1 * value))) %>% 
  mutate(patient = factor(x = patient, 
                          levels = c("Patient with low PEDIS Score", "Patient with high PEDIS Score"),
                          ordered = TRUE))

mean_summary <- data %>% 
  group_by(patient) %>% 
  summarise(avg = mean(value))

data %>% 
  ggplot(aes(x = value, y = ..density.., fill = patient)) +
  geom_histogram(binwidth = .01) +
  scale_y_continuous("Density") +
  scale_x_continuous("Probability", limits = c(-0.05, .5)) +
  geom_vline(data = mean_summary,
             aes(xintercept = avg, col = patient),
             linetype = 5, 
             size = 1.5) +
  ggtitle("Histogram of Posterior Amputation Probability") +
  scale_fill_manual(values = c("grey30", "grey50")) +
  scale_color_manual(values = c("black", "black"), guide = F) +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.title = element_blank())

ggsave(filename = "./img/post-amp-major-prob.png", units = "cm", width = 22, height = 22)

```

# Appendix

## MCMC Ketten

```{r, eval=FALSE}

plot_mcmc <- function(model, color_scheme = "gray", outcome = "any_amputation") {
  
  posterior <- as.array(model)
  
  color_scheme_set(color_scheme)
  
  bayesplot::mcmc_trace(posterior, pars = c("p", "e_ordinal_5", "d", "i", "s"),
                        facet_args = list(ncol = 1, strip.position = "top")) +
    theme_pubr() +
    scale_y_continuous(limits = c(-0.6, 2)) +
    theme(legend.position = "left")

  ggsave(filename = paste0("img/mcmc-trace-posterior-", outcome, ".png"))
         
}

models <- list(noninformed_any, informed_any, noninformed_major, informed_major)
models_title <- c("amp-any-noninfo", "amp-any-info", "amp-maj-noninfo", "amp-major-info") 

map2(models, models_title, function(m, col) plot_mcmc(pluck(m, 4), outcome = col))

```

```{r, eval = F}

hypos <- brms::hypothesis(noninformed_any[[4]], "d > 0")
sum_any <- summary(noninformed_any[[4]], digits = 3)

```

## AUC Differences

```{r}

# Among uninformative priors
auc_df <- auc %>% 
  enframe %>% 
  unnest(value)

auc_df %>% 
  group_by(name) %>% 
  summarise(avg = median(value))

cohen <- auc_df %>% 
  filter(grepl(pattern = "Non", x = name)) %>% 
  effsize::cohen.d(value ~ name, data = .) %>% 
  pluck("estimate")

delta <- auc_df %>% 
  filter(grepl(pattern = "Non", x = name)) %>%
  group_by(name) %>% 
  summarise(avg = mean(value)) %>% 
  pull(avg) %>% 
  diff

enframe(c(cohen = cohen, delta = delta)) %>% 
  kable(digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)

```
```{r}

cohen <- auc_df %>% 
  filter(grepl(pattern = "Any", x = name)) %>%
  effsize::cohen.d(value ~ name, data = .) %>% 
  pluck("estimate")

delta <- auc_df %>% 
  filter(grepl(pattern = "Any", x = name)) %>%
  group_by(name) %>% 
  summarise(avg = mean(value)) %>% 
  pull(avg) %>% 
  diff

enframe(c(cohen = cohen, delta = delta)) %>% 
  kable(digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)

```

```{r}

cohen <- auc_df %>% 
  filter(grepl(pattern = "Major", x = name)) %>%
  effsize::cohen.d(value ~ name, data = .) %>% 
  pluck("estimate")

delta <- auc_df %>% 
  filter(grepl(pattern = "Major", x = name)) %>%
  group_by(name) %>% 
  summarise(avg = mean(value)) %>% 
  pull(avg) %>% 
  diff

enframe(c(cohen = cohen, delta = delta)) %>% 
  kable(digits = 3) %>%
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)

```

## Collinearity

```{r}
pedis_class <- pedis %>% select(p, e_ordinal_5, d, i, s)
cor(pedis_class, method = "kendall")

chains <- map(models, pluck, 2)

chains <- chains %>% 
  map(select, c("Perfusion", "Extend", "Depth", "Infection", "Sensation")) 

pred <- c("Perfusion", "Extend", "Depth", "Infection", "Sensation")
bayesplot::mcmc_scatter(as.matrix(chains[[1]]), pars = pred[1:2], alpha = .2)
scatter_style_np(div_color = "red", div_shape = 16, div_size = 2.5,
  div_alpha = .1)

bayesplot::mcmc_pairs(as.matrix(chains[[1]][1:100, ]), pars = pred[1:2])

library(GGally)  
ggpairs(chains[[1]][1:100, ])


```

# Univariate Association

```{r}

outcome <- c("any_amputation", "major_amputation")
predictors <- c("p", "e_ordinal_5", "d", "i", "s", "alter_bei_aufnahme", "gender")

formulas <- expand.grid(outcome = outcome, predictors = predictors) %>% 
  as_tibble() %>% 
  unite(col = formula, c("outcome", "predictors"), sep = " ~ ") %>% 
  pull(1) %>% 
  as.list()


univar_association <- function(formula) {
  
  set.seed(1231238)
  
  model <- rstanarm::stan_glm(formula = as.formula(formula),
                              family = "binomial",
                              data = pedis,
                              prior = cauchy(location = 0, scale = 0.5))
  
  intervals <- hdi(x = model, ci = .95) %>% 
    as.tibble() %>% 
    filter(!grepl(pattern = "Intercept", x = Parameter)) 
  
  params <- as.matrix(x = model) %>% 
    as.tibble() %>% 
    select(2) %>% 
    summarise_all(list(odds_ratio = function(x) exp(median(x)),
                       coefficient = function(y) median(y)))
  
  posterior <- as.matrix(model) %>% 
    as.tibble %>% 
    rename(values = 2) %>% 
    select(2) %>% 
    nest(data = everything())
  
  outcome <- str_extract(string = formula, pattern = "(.*)_amputation")
  outcome <- enframe(outcome, name = "outcome")
  
  bind_cols(params, intervals, posterior, outcome)
  
}

univariate_coefficients <- map_df(formulas, univar_association)



```

```{r out.width='100%'}
lvls <- c("p", "e_ordinal_5", "d", "i", "s", "alter_bei_aufnahme", "gender")
lbls <- c("Perfusion", 
          "Extent", 
          "Depth", 
          "Infection", 
          "Sensation", 
          "Age", 
          "Gender")

univar_analysis <- univariate_coefficients %>% 
  arrange(value) %>% 
  mutate(Parameter = factor(x = Parameter, 
                            levels = lvls,
                            labels = lbls,
                            ordered = TRUE)) %>% 
  mutate(value = factor(x = value, 
                        levels = c("any_amputation", "major_amputation"), 
                        labels = c("Any Amputation", "Major Amputation"),
                        ordered = TRUE)) %>% 
  mutate(CI_low_exp = exp(CI_low), CI_high_exp = exp(CI_high))
  
univar_analysis %>% 
  ggplot(aes(x = forcats::fct_rev(Parameter), y = coefficient, ymin = CI_low, ymax = CI_high)) +
  geom_point() +
  geom_errorbar(width = .2) +
  geom_abline(intercept = 0, slope = 0, size = .2, linetype = 2) +
  facet_wrap(~ value, ncol = 1) +
  coord_flip(clip = "off") +
  scale_y_continuous("Coefficients", breaks = seq(-1, 3, by = .5)) +
  theme_bw() +
  theme(axis.title.y = element_blank()) +
  ggtitle("Coefficients of Univariate Logistic Models")

# Din A4 210 × 297 millimeters (Half)
ggsave(filename = "img/appendix-univar-models.png",
       units = "cm",
       height = 29.7 / 2, width = 21.0 / 2, 
       dpi = 300)

univar_analysis <- univar_analysis %>% 
  mutate_if(is.numeric, sprintf, fmt = "%1.3f") %>% 
  mutate(coef_hdi = glue::glue("{coefficient} [{CI_low} to {CI_high}]")) %>% 
  mutate(or_hdi = glue::glue("{odds_ratio} [{CI_low_exp} to {CI_high_exp}]")) %>% 
  mutate_at("coef_hdi", as.character) %>% 
  select(Parameter, value, coef_hdi, or_hdi, starts_with("CI"), odds_ratio, coefficient)

sheets_write(data = univar_analysis %>% arrange(value),
             ss = googlesheet_id,
             sheet = "univar-analysis")

```

## Model Diagnostics


We created Bayesian Logistic Regression models using the open-source **rstanarm** package for the statistical programming language R.

Our model analyzes the relationship between the PEDIS-system, a clinical classification to describe characteristics of Diabetic Foot Ulcers, and amputation, which results from such ulcers as a severe complication. 

We used two distinct amputation definitions: 

1. Any Amputation excluding the lesser toes (This definition entails minor and major amputation, whereas major amputations are on the level of the lower limb or even more proximal, e.g., knee or thigh). 

Furthermore, we scrutinized the impact of an informed prior compared to a non-informed one.

As a result, we created four distinct model.

1. Non-informed with any-amputation
2. Non-informed with major-amputation
3. Informed with any-amputation
4. Informed with major-amputation

### Non-informed Models

#### Any Major

```{r}

model_any_non <- readRDS("models/any-amputation-non-informed.RDS") %>% pluck(4)

color_scheme_set("viridis")

# Effect size
ess_any_non <- summary(model_any_non) %>% 
  as.data.frame() %>% 
  as_tibble(rownames = "Predictors") %>% 
  select(Predictors, any_non = n_eff) %>% 
  slice(1:8)

# MCMC trace
mcmc_trace(model_any_non)

# Scatterplots of MCMC draws
mcmc_pairs(x = model_any_non, pars = c("p", "e_ordinal_5", "d", "i", "s"))


# Posterior predictive check
pp_check(model_any_non)

```


#### Any Amputation Informed

```{r}

model_major_non <- readRDS("models/major-amputation-non-informed.RDS") %>% pluck(4)

color_scheme_set("viridis")

# Effect size
ess_major_non <- summary(model_major_non) %>% 
  as.data.frame() %>% 
  as_tibble(rownames = "Predictors") %>% 
  select(Predictors, major_non = n_eff) %>% 
  slice(1:8)

# MCMC trace
mcmc_trace(model_major_non)

# Scatterplots of MCMC draws
mcmc_pairs(x = model_major_non, pars = c("p", "e_ordinal_5", "d", "i", "s"))


# Posterior predictive check
pp_check(model_major_non)

```

### Informed Models

#### Any Amputation

```{r}

model_any_inf <- readRDS("models/any-amputation-informed.RDS") %>% pluck(4)

color_scheme_set("viridis")

# Effect size
ess_any_inf <- summary(model_any_inf) %>% 
  as.data.frame() %>% 
  as_tibble(rownames = "Predictors") %>% 
  select(Predictors, any_inf = n_eff) %>% 
  slice(1:8) 

# MCMC trace
mcmc_trace(model_any_inf)

# Scatterplots of MCMC draws
mcmc_pairs(x = model_any_inf, pars = c("p", "e_ordinal_5", "d", "i", "s"))


# Posterior predictive check
pp_check(model_any_inf)

```

#### Major Amputation

```{r}

model_major_inf <- readRDS("models/major-amputation-informed.RDS") %>% pluck(4)

color_scheme_set("viridis")

# Effect size
ess_major_inf <- summary(model_major_inf) %>% 
  as.data.frame() %>% 
  as_tibble(rownames = "Predictors") %>% 
  select(Predictors, major_inf = n_eff) %>% 
  slice(1:8)

# MCMC trace
mcmc_trace(model_major_inf)

# Scatterplots of MCMC draws
mcmc_pairs(x = model_major_inf, pars = c("p", "e_ordinal_5", "d", "i", "s"))


# Posterior predictive check
pp_check(model_major_inf)

```

```{r}

ess <- list(ess_any_non, ess_any_inf, ess_major_non, ess_major_inf) %>% 
  reduce(inner_join, by = "Predictors")

ess %>% 
  kable() %>% 
  kableExtra::kable_styling(bootstrap_options = "striped", full_width = F)

sheets_write(data = ess,
             ss = googlesheet_id,
             sheet = "ess")


```

