---
title: "Appendix"
author: "Jens Hüsers"
date: "3/6/2020"
output: html_document
editor_options: 
  chunk_output_type: console
  fig_width: 6 
  fig_height: 4 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

knitr::opts_chunk$set(echo = TRUE,  
                      cache = TRUE,
                      warning = FALSE,
                      message = FALSE,
                      out.width = '100%',
                      fig.pos = 'center')

set.seed(2430024)

date <- lubridate::now()
format(date, "%a, %d. %B %Y")

# Load Packages
library(broman)
library(tidyverse)
library(knitr)
library(googlesheets4)
library(scales)
library(ggpubr)
library(magick)
library(gridExtra)
library(bayesplot)

predictors <- c("Perfusion", "Extend", "Depth", "Infection", "Sensation", "Age", "Gender")

```


```{r}
# Load MCMC samples

files <- dir("models")
file <- files[grepl(x = files, pattern = "RDS$")]
filepath <- glue::glue("models/backup-mcmc/{file}")

informed_any <- readRDS(filepath[1])
noninformed_any <- readRDS(filepath[2])
informed_major <- readRDS(filepath[3])
noninformed_major <- readRDS(filepath[4])

```

# Non Informed Model for Any-Amputation

```{r}
# assign the model
model <- noninformed_any[[4]]

```


## Effective Sample Size

The effective sample size and the effective sample size in comparison to the actual sample size.

```{r}

summary(model) %>% 
  as.data.frame() %>% 
  as_tibble(rownames = "Predictors") %>% 
  select(Predictors, any_non = n_eff) %>% 
  slice(1:8) %>% 
  kable()

neff_ratio(model) %>% kable()

```

## Autorcorrelation in the MCMC chains

Autocorrelation shown with lag plots and trace plots

```{r}

mcmc_acf(as.matrix(model), lags = 10)

style <- trace_style_np(div_alpha = .1, div_size = 0.01)

mcmc_trace(as.array(model),
                n_warmup = 500,
                np_style = style) 

```

## Collinearity of the Predictors

Investigtion of colliniearity with scatter- and hex plots.

```{r}

mcmc_pairs(as.matrix(model), off_diag_fun = c("scatter"),
           off_diag_args = list(alpha = .01, size = .5))

mcmc_pairs(as.matrix(model), off_diag_fun = c("hex"),
           off_diag_args = list(alpha = .01, size = .5))


cov <- cor(as.matrix(model), method = "pearson")
colnames(cov) <- c("ic", "p", "e", "d", "i", "s", "a", "g")

diag(cov) <- NA
max(abs(cov)[-1, -1], na.rm = TRUE)

diag(cov) <- 1

kable(cov)

```

## Posterior Predictive Checks

```{r}

color_scheme_set("red")

ppc_dens_overlay(y = model$y,
                 yrep = posterior_predict(model, draws = 50))

``` 



# Informed Model for Any-Amputation

```{r}
# assign the model
model <- informed_any[[4]]

```


## Effective Sample Size

The effective sample size and the effective sample size in comparison to the actual sample size.

```{r}

summary(model) %>% 
  as.data.frame() %>% 
  as_tibble(rownames = "Predictors") %>% 
  select(Predictors, any_non = n_eff) %>% 
  slice(1:8) %>% 
  kable()

neff_ratio(model) %>% kable()

```

## Autorcorrelation in the MCMC chains

Autocorrelation shown with lag plots and trace plots

```{r}

mcmc_acf(as.matrix(model), lags = 10)

style <- trace_style_np(div_alpha = .1, div_size = 0.01)

mcmc_trace(as.array(model),
                n_warmup = 500,
                np_style = style) 

```

## Collinearity of the Predictors

Investigtion of colliniearity with scatter- and hex plots.

```{r}

mcmc_pairs(as.matrix(model), off_diag_fun = c("scatter"),
           off_diag_args = list(alpha = .01, size = .5))

mcmc_pairs(as.matrix(model), off_diag_fun = c("hex"),
           off_diag_args = list(alpha = .01, size = .5))


cov <- cor(as.matrix(model), method = "pearson")
colnames(cov) <- c("ic", "p", "e", "d", "i", "s", "a", "g")

diag(cov) <- NA
max(abs(cov)[-1, -1], na.rm = TRUE)

diag(cov) <- 1

kable(cov)

```

## Posterior Predictive Checks

```{r}

color_scheme_set("red")

ppc_dens_overlay(y = model$y,
                 yrep = posterior_predict(model, draws = 50))

``` 


# Non Informed Model for Major-Amputation

```{r}
# assign the model
model <- noninformed_major[[4]]

```


## Effective Sample Size

The effective sample size and the effective sample size in comparison to the actual sample size.

```{r}

summary(model) %>% 
  as.data.frame() %>% 
  as_tibble(rownames = "Predictors") %>% 
  select(Predictors, any_non = n_eff) %>% 
  slice(1:8) %>% 
  kable()

neff_ratio(model) %>% kable()

```

## Autorcorrelation in the MCMC chains

Autocorrelation shown with lag plots and trace plots

```{r}

mcmc_acf(as.matrix(model), lags = 10)

style <- trace_style_np(div_alpha = .1, div_size = 0.01)

mcmc_trace(as.array(model),
                n_warmup = 500,
                np_style = style) 

```

## Collinearity of the Predictors

Investigtion of colliniearity with scatter- and hex plots.

```{r}

mcmc_pairs(as.matrix(model), off_diag_fun = c("scatter"),
           off_diag_args = list(alpha = .01, size = .5))

mcmc_pairs(as.matrix(model), off_diag_fun = c("hex"),
           off_diag_args = list(alpha = .01, size = .5))


cov <- cor(as.matrix(model), method = "pearson")
colnames(cov) <- c("ic", "p", "e", "d", "i", "s", "a", "g")

diag(cov) <- NA
max(abs(cov)[-1, -1], na.rm = TRUE)

diag(cov) <- 1

kable(cov)

```

## Posterior Predictive Checks

```{r}

color_scheme_set("red")

ppc_dens_overlay(y = model$y,
                 yrep = posterior_predict(model, draws = 50))

``` 


# Informed Model for Major-Amputation

```{r}
# assign the model
model <- informed_major[[4]]

```


## Effective Sample Size

The effective sample size and the effective sample size in comparison to the actual sample size.

```{r}

summary(model) %>% 
  as.data.frame() %>% 
  as_tibble(rownames = "Predictors") %>% 
  select(Predictors, any_non = n_eff) %>% 
  slice(1:8) %>% 
  kable()

neff_ratio(model) %>% kable()

```

## Autorcorrelation in the MCMC chains

Autocorrelation shown with lag plots and trace plots

```{r}

mcmc_acf(as.matrix(model), lags = 10)

style <- trace_style_np(div_alpha = .1, div_size = 0.01)

mcmc_trace(as.array(model),
                n_warmup = 500,
                np_style = style) 

```

## Collinearity of the Predictors

Investigtion of colliniearity with scatter- and hex plots.

```{r}

mcmc_pairs(as.matrix(model), off_diag_fun = c("scatter"),
           off_diag_args = list(alpha = .01, size = .5))

mcmc_pairs(as.matrix(model), off_diag_fun = c("hex"),
           off_diag_args = list(alpha = .01, size = .5))


cov <- cor(as.matrix(model), method = "pearson")
colnames(cov) <- c("ic", "p", "e", "d", "i", "s", "a", "g")

diag(cov) <- NA
max(abs(cov)[-1, -1], na.rm = TRUE)

diag(cov) <- 1

kable(cov)

```

## Posterior Predictive Checks

```{r}

color_scheme_set("red")

ppc_dens_overlay(y = model$y,
                 yrep = posterior_predict(model, draws = 50))

``` 